### 2017-02-03 paper1.tex
THESIS TO COMMITTEE

\chapter[Solar control of \(F\) region radar backscatter: Further insights from observations in the southern polar cap]{Solar control of \(F\) region radar backscatter: Further insights from observations in the southern polar cap\footnote{Published as: {Lamarche}, L.~J., and R.~A. {Makarevich} (2015), Solar control of {F} region radar backscatter: Further insights from observations in the southern polar cap, \textit{J. Geophys. Res. Space Physics}, \textit{120}(11), 9875--9890, \doi{10.1002/2015JA021663}.}}

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f1.pdf}
	\caption[Monthly average echo occurrence and electron density]{Monthly average plots of (a--d) echo occurrence and (e--h) peak electron density for 2010.  Four months are selected (one for each season) to show seasonal variations. In Figures \ref{fig:month_avg_occ}a--\ref{fig:month_avg_occ}d,  the pink line shows the 25\% occurrence contour that is used to define the echo band region. Black dots are the midpoints between the upper and lower portion of this contour.  A cosine function (white line) is fit to these points and used to model the echo band. The dashed white lines are the upper and lower bounds of the model band. The top right corner of each panel shows the parameters that characterize the band for that month: \(A\) is amplitude of cosine function, \(B\) is time shift, \(C\) is range shift from 0, and BW is the band width.  In Figures \ref{fig:month_avg_occ}e--\ref{fig:month_avg_occ}h the same echo location model is also given (white lines) along with expected echo locations based on ray tracing simulations (solid lines).  The red (grey) lines refer to three URSI (CCIR) options (see text for details).}
	\label{fig:month_avg_occ}
\end{figure}

@@

The final observation about Figure \ref{fig:month_avg_occ} concerns the results of raytracing simulations that were conducted for each hour of day 15 in each of the four months shown in Figure \ref{fig:month_avg_occ} using a version of standard ray tracing tools based on numerical solutions of the Hamiltonian raypath equations \citep{Haselgrove1963,Jones1975} that allow the consideration of arbitrary density distributions. In these simulations, IRI densities in a 2-D simulation domain aligned with beam 14 of MCM were used.  That is, plasma densities employed were varying both horizontally and vertically.  The grid bins in the horizontal and vertical directions were 5 km and 1 km, respectively, which is well below the radar cell size of 45 km.  Rays separated by \(1\deg\) in elevation were found under the assumption of ordinary mode propagation.  Locations were founds where the ray was nearly perpendicular (within \(1\deg\)) to the local magnetic field based on the International Geomagnetic Reference Field 12 model \citep{Thebault2015}.

@@

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f2.pdf}
	\caption[Trends in high-occurrence band]{The variations in the echo band (a) amplitude of the fitted cosine function \(A\), (b) time shift or time of day of the peak \(B\), (c) average position of the band or the vertical shift of the cosine function from zero \(C\), and (d) width (BW). Different lines are for different years with the legend given in Figure \ref{fig:year_line}a.  The fit errors are given by the vertical bars.}
	\label{fig:year_line}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f3.pdf}
	\caption[Solar cycle trends of high-occurrence band]{Contour plots of the (a--d) echo band position \(r(t)\) and (e)--(h) occurrence versus UT and season. Each row shows the data for a different year as given in the top right corner.  The unfilled color contours in Figures \ref{fig:year_color}a--\ref{fig:year_color}d show the fitted band position \(R(t)\) using the same color scheme.}
	\label{fig:year_color}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{p1f4.pdf}
	\caption[Band position and occurrence versus SZA and \(N_mF_2\)]{The echo band range versus the (a) solar zenith angle (SZA) and (b) model peak F2 electron density (\(N_mF_2\)). Each point is color-coded in model \(E\) region density. Figures \ref{fig:scatter}c and \ref{fig:scatter}d show the same as Figures \ref{fig:scatter}a and \ref{fig:scatter}b but for the  echo occurrence within the band.}
	\label{fig:scatter}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{p1f5.pdf}
	\caption[Occurrence versus UT and IMF conditions]{The MCM echo occurrence versus UT color coded in the average (a) IMF \(B_y\), (b) IMF \(B_z\), and (c) PCS values.}
	\label{fig:ut_occ}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{p1f6.pdf}
	\caption[An example of conjugate observations of patchy backscatter]{Conjugate measurements for two selected events on (a--d) March 14, 2010 and (e-h) April 6, 2010. Shown are the IMF \(B_y\) (blue) and \(B_z\) (red) components (Figures \ref{fig:patchy_example}a and \ref{fig:patchy_example}e), MCM line-of-sight velocity versus UT and slant range in beam 14 (Figures \ref{fig:patchy_example}b and \ref{fig:patchy_example}f), RKN velocity in beam 4 (Figure \ref{fig:patchy_example}c and \ref{fig:patchy_example}g), and RISR-N electron density versus UT and altitude (Figure \ref{fig:patchy_example}d and \ref{fig:patchy_example}h). The color bar is the same for Figures \ref{fig:patchy_example}b, \ref{fig:patchy_example}f, \ref{fig:patchy_example}c, and \ref{fig:patchy_example}g and is given to the right of Figure \ref{fig:patchy_example}f.}
	\label{fig:patchy_example}
\end{figure}

@@

The backscatter patches move away form MCM in Figure \ref{fig:patchy_example}b.  For example, the patch near 17 UT moved by \(\sim700\) km in \(\sim\)20-min, which translates into \(\sim600\) m/s velocity.  This is consistent with the Doppler velocity measured by MCM within the patch (dark blue colors).  Similar consistency between the patch drift and plasma convection velocities was observed by \citet{Bristow2011} using MCM observations and, more recently, by \citet{Makarevich2015} using direct observations of 2-D convection velocity and density enhancements by RISR-N in the northern polar cap.  This impolies that polar patches tend to move with the background convection, at least deep within the polar cap.

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f7.pdf}
	\caption[Summary of annual and diurnal variations]{Contour plots of the (a) average occurrence within the band, (b) band range, (c) model peak F-region electron density (\(N_mF_2\)) and (d) solar zenith angle (SZA) versus UT and month in 2010. Color bars are given to the right. The white rectangle at the bottom of each panel is due to no data available in January 2010.}
	\label{fig:month_ut}
\end{figure}

>>>>

\chapter[Solar Control of \(F\) Region Radar Backscatter: Further Insights from Observations in the Southern Polar Cap]{Solar Control of \(F\) Region Radar Backscatter: Further Insights from Observations in the Southern Polar Cap\footnote{Published as: {Lamarche}, L.~J., and R.~A. {Makarevich} (2015), Solar control of {F} region radar backscatter: Further insights from observations in the southern polar cap, \textit{J. Geophys. Res. Space Physics}, \textit{120}(11), 9875--9890, \doi{10.1002/2015JA021663}.}}

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f1.pdf}
	\caption[Monthly average echo occurrence and electron density]{{\:}Monthly average echo occurrence and electron density\\ Monthly average plots of (a--d) echo occurrence and (e--h) peak electron density for 2010.  Four months are selected (one for each season) to show seasonal variations. In Figures \ref{fig:month_avg_occ}a--\ref{fig:month_avg_occ}d,  the pink line shows the 25\% occurrence contour that is used to define the echo band region. Black dots are the midpoints between the upper and lower portion of this contour.  A cosine function (white line) is fit to these points and used to model the echo band. The dashed white lines are the upper and lower bounds of the model band. The top right corner of each panel shows the parameters that characterize the band for that month: \(A\) is amplitude of cosine function, \(B\) is time shift, \(C\) is range shift from 0, and BW is the band width.  In Figures \ref{fig:month_avg_occ}e--\ref{fig:month_avg_occ}h the same echo location model is also given (white lines) along with expected echo locations based on ray tracing simulations (solid lines).  The red (grey) lines refer to three URSI (CCIR) options (see text for details).}
	\label{fig:month_avg_occ}
\end{figure}

@@

The final observation about Figure \ref{fig:month_avg_occ} concerns the results of raytracing simulations that were conducted for each hour of day 15 in each of the four months shown in Figure \ref{fig:month_avg_occ} using a version of standard ray tracing tools based on numerical solutions of the Hamiltonian raypath equations \citep{Haselgrove1963,Jones1975} that allow the consideration of arbitrary density distributions. In these simulations, IRI densities in a 2D simulation domain aligned with beam 14 of MCM were used.  That is, plasma densities employed were varying both horizontally and vertically.  The grid bins in the horizontal and vertical directions were 5 km and 1 km, respectively, which is well below the radar cell size of 45 km.  Rays separated by \(1\deg\) in elevation were found under the assumption of ordinary mode propagation.  Locations were founds where the ray was nearly perpendicular (within \(1\deg\)) to the local magnetic field based on the International Geomagnetic Reference Field 12 model \citep{Thebault2015}.

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f2.pdf}
	\caption[Trends in high-occurrence band]{{\:}Trends in high-occurrence band\\ The variations in the echo band (a) amplitude of the fitted cosine function \(A\), (b) time shift or time of day of the peak \(B\), (c) average position of the band or the vertical shift of the cosine function from zero \(C\), and (d) width (BW). Different lines are for different years with the legend given in Figure \ref{fig:year_line}a.  The fit errors are given by the vertical bars.}
	\label{fig:year_line}
\end{figure}

@@

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f3.pdf}
	\caption[Solar cycle trends of high-occurrence band]{{\:}Solar cycle trends of high-occurrence band\\ Contour plots of the (a--d) echo band position \(r(t)\) and (e)--(h) occurrence versus UT and season. Each row shows the data for a different year as given in the top right corner.  The unfilled color contours in Figures \ref{fig:year_color}a--\ref{fig:year_color}d show the fitted band position \(R(t)\) using the same color scheme.}
	\label{fig:year_color}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{p1f4.pdf}
	\caption[Band position and occurrence versus SZA and \(N_mF_2\)]{{\:}Band position and occurrence versus SZA and \(N_mF_2\)\\ The echo band range versus the (a) solar zenith angle (SZA) and (b) model peak F2 electron density (\(N_mF_2\)). Each point is color-coded in model \(E\) region density. Figures \ref{fig:scatter}c and \ref{fig:scatter}d show the same as Figures \ref{fig:scatter}a and \ref{fig:scatter}b but for the  echo occurrence within the band.}
	\label{fig:scatter}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{p1f5.pdf}
	\caption[Occurrence versus UT and IMF conditions]{{\:}Occurrence versus UT and IMF conditions\\ The MCM echo occurrence versus UT color coded in the average (a) IMF \(B_y\), (b) IMF \(B_z\), and (c) PCS values.}
	\label{fig:ut_occ}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{p1f6.pdf}
	\caption[An example of conjugate observations of patchy backscatter]{{\:}An example of conjugate observations of patchy backscatter\\ Conjugate measurements for two selected events on (a--d) March 14, 2010 and (e-h) April 6, 2010. Shown are the IMF \(B_y\) (blue) and \(B_z\) (red) components (Figures \ref{fig:patchy_example}a and \ref{fig:patchy_example}e), MCM line-of-sight velocity versus UT and slant range in beam 14 (Figures \ref{fig:patchy_example}b and \ref{fig:patchy_example}f), RKN velocity in beam 4 (Figure \ref{fig:patchy_example}c and \ref{fig:patchy_example}g), and RISR-N electron density versus UT and altitude (Figure \ref{fig:patchy_example}d and \ref{fig:patchy_example}h). The color bar is the same for Figures \ref{fig:patchy_example}b, \ref{fig:patchy_example}f, \ref{fig:patchy_example}c, and \ref{fig:patchy_example}g and is given to the right of Figure \ref{fig:patchy_example}f.}
	\label{fig:patchy_example}
\end{figure}

@@

The backscatter patches move away form MCM in Figure \ref{fig:patchy_example}b.  For example, the patch near 17 UT moved by \(\sim700\) km in \(\sim\)20-min, which translates into \(\sim600\) m/s velocity.  This is consistent with the Doppler velocity measured by MCM within the patch (dark blue colors).  Similar consistency between the patch drift and plasma convection velocities was observed by \citet{Bristow2011} using MCM observations and, more recently, by \citet{Makarevich2015} using direct observations of 2D convection velocity and density enhancements by RISR-N in the northern polar cap.  This impolies that polar patches tend to move with the background convection, at least deep within the polar cap.

@@

\begin{figure}
	\centering
	\includegraphics[height=\textwidth,angle=90]{p1f7.pdf}
	\caption[Summary of annual and diurnal variations]{{\:}Summary of annual and diurnal variations\\ Contour plots of the (a) average occurrence within the band, (b) band range, (c) model peak F-region electron density (\(N_mF_2\)) and (d) solar zenith angle (SZA) versus UT and month in 2010. Color bars are given to the right. The white rectangle at the bottom of each panel is due to no data available in January 2010.}
	\label{fig:month_ut}
\end{figure}

### 2017-02-03 paper2.tex
THESIS TO COMMITTEE

\chapter[A modeling study of asymmetries in plasma irregularity characteristics near gradient reversals]{A modeling study of asymmetries in plasma irregularity characteristics near gradient reversals\footnote{Published as: {Lamarche}, L.~J., and R.~A. {Makarevich} (2016), A modeling study of asymmetries in plasma irregularity characteristics near gradient reversals, \textit{Ann. Geophysicae}, \textit{34}, 709--723, \doi{10.5194/angeo-34-709-2016}.}}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f1.pdf}
	\caption[Overview of altitudinal variations and model setup of MCM]{(a) Altitudinal variations of parameters of interest. Shown are the ratios of collision frequencies and gyrofrequencies for electrons \(-r_e=\nu_e/|\Omega_e|\) (blue) and ions \(r_i=\nu_i/\Omega_i\) (green), the anisotropy parameter \(\psi=-r_i r_e\) (pink), and the conductivity ratio \(R=\sigma_H/\sigma_P = \left(r_i+r_e\right)/\left(1+\psi\right)\) (dashed black line on top of the green one).  (b) Virtual height of radar scattering volume versus the slant range. The areas shaded with red, green, and blue color refer to the \(E\) region, transitional region, and \(F\) region, respectively. (c) Geometry of observations and the gradient-drift instability (GDI) growth rate pattern in the radar's field-of-view (FoV). The plasma density gradient reversal is shown by the the heavy white line. The gradient vectors \(\vec{G}=\nabla n_0/n_0\) point towards the reversal in all points within the FoV as shown by representative pink vectors. Also shown are the angle \(\theta\) between the gradient reversal and the horizontal axis (dashed black line),  the angle \(\phi\) between the convection velocity direction \(\vec{V}_E\) (red arrow) and the horizontal axis. The electric field \(\vec{E}\)  and the wave vector  \(\vec{k}\) are shown by the green and yellow arrows, respectively. The normalized GDI growth rate at every cell in the radar's FoV was calculated and the radar cells are colored accordingly, with the color bar shown in the bottom-right corner.  The \(E\) region, transitional region, and \(F\) region are outlined in red, green, and blue, respectively.}
	\label{fig:model_setup}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{p2f2.pdf}
	\caption[GDI growth rate within radar FoV]{The GDI growth rate within the radar's FoV for four cases of gradient reversal orientation and position (white line).  In all cases, the convection direction \(\vec{V}_E\) (red arrow) is perpendicular to the gradient reversal direction.  The orientation of the vectors \(\vec{G}\), \(\vec{V}_E\), \(\vec{E}\), and \(\vec{k}\) are shown in each panel, using the same colors as in Figure \ref{fig:model_setup}c.  The GDI growth rate at each radar cell is given by the cell color, with the color bar given in the bottom-left corner of panel (a). Panels (a) and (b) show a gradient reversal centered in the \(F\) region, while panels (c) and (d) show the reversal in the transitional region.  The angles \(\theta\) and \(\phi\) (as defined in Figure \ref{fig:model_setup}c) are also given in the bottom-right corner of each panel.}
	\label{fig:fov_grs}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f3.pdf}
	\caption[GDI growth rates for set angle between \(\vec{V}_E\) and \(\vec{G}\)]{The difference in the GDI growth rate across the gradient reversal for four selected angles between the reversal and convection direction.  The gradient reversal direction \(\theta\) is on the \(x\)-axis and the average growth rate difference across the reversal \(\Delta\gamma\) is on the \(y\)-axis for each panel.  The difference between \(\phi\) and \(\theta\) is given in the top-right corner of each plot. The difference in the average growth rate \(\Delta\gamma\) computed using a numerical approach (see text for details) is shown by the solid lines, with the shaded regions representing the standard deviation.  The dashed lines show the behavior of \(\Delta\gamma\) calculated using an analytic expression. The trends for both the \(E\)-region (red) and \(F\)-region (blue) cases are shown in each panel.}
	\label{fig:set_angle}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f4.pdf}
	\caption[GDI growth rates for arbitrary angle between \(\vec{V}_E\) and \(\vec{G}\)]{Contour plots of the growth rate difference \(\Delta\gamma\)  versus the two angles of interest. The direction of the gradient reversal \(\theta\) is on the \(x\)-axis and the convection direction \(\phi\) is on the \(y\)-axis.  The color bar is given to the right. Panels (a) and (b) show the results using an analytic approach in the \(E\) and \(F\) regions, respectively.  Panels (c)--(f) show the results using a numerical approach in the \(E\), \(F\), transitional, and all regions, respectively. The dashed black and white line in panels (c) and (f) indicates the average value of the conductivity ratio \(R\) along the gradient reversal for different angles \(\theta\) in the transitional region and all regions, respectively. The scale for \(R\) is shown on the right of panels (c) and (f).}
	\label{fig:any_angle}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f5.pdf}
	\caption[GDI growth rate within transitional region]{Analysis of the transitional region.  (a) The average conductivity ratio \(R\) (black line) and the radar virtual height (orange line) versus the slant range for the entire transitional region and parts of the \(E\) and \(F\) regions. The scales for the conductivity ratio and height are given on the left and right of panel (a), respectively.  The \(E\) (red), transitional (yellow and green) and \(F\) (blue) regions are highlighted.  The region highlighted with yellow is examined closer in panels (b) and (c).  Panel (b) is similar to panel (a), but focuses on slant ranges 600--616 km, where most of the change in the conductivity ratio occurs.  In addition to the \(R\) and height continuous variations, it also gives the average value of \(R\) for each 2-km virtual range gate. The same 2-km virtual gates are considered in panel (c) that shows a similar analysis to Figure \ref{fig:any_angle}. The top row shows the results of the numerical approach (N) and the bottom row shows the analytic approach results (A).}
	\label{fig:transitional}
\end{figure}

>>>>

\chapter[A Modeling Study of Asymmetries in Plasma Irregularity Characteristics Near Gradient Reversals]{A Modeling Study of Asymmetries in Plasma Irregularity Characteristics Near Gradient Reversals\footnote{Published as: {Lamarche}, L.~J., and R.~A. {Makarevich} (2016), A modeling study of asymmetries in plasma irregularity characteristics near gradient reversals, \textit{Ann. Geophysicae}, \textit{34}, 709--723, \doi{10.5194/angeo-34-709-2016}.}}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f1.pdf}
	\caption[Overview of altitudinal variations and model setup of MCM]{{\:}Overview of altitudinal variations and model setup of MCM\\ (a) Altitudinal variations of parameters of interest. Shown are the ratios of collision frequencies and gyrofrequencies for electrons \(-r_e=\nu_e/|\Omega_e|\) (blue) and ions \(r_i=\nu_i/\Omega_i\) (green), the anisotropy parameter \(\psi=-r_i r_e\) (pink), and the conductivity ratio \(R=\sigma_H/\sigma_P = \left(r_i+r_e\right)/\left(1+\psi\right)\) (dashed black line on top of the green one).  (b) Virtual height of radar scattering volume versus the slant range. The areas shaded with red, green, and blue color refer to the \(E\) region, transitional region, and \(F\) region, respectively. (c) Geometry of observations and the gradient-drift instability (GDI) growth rate pattern in the radar's field-of-view (FoV). The plasma density gradient reversal is shown by the the heavy white line. The gradient vectors \(\vec{G}=\nabla n_0/n_0\) point towards the reversal in all points within the FoV as shown by representative pink vectors. Also shown are the angle \(\theta\) between the gradient reversal and the horizontal axis (dashed black line),  the angle \(\phi\) between the convection velocity direction \(\vec{V}_E\) (red arrow) and the horizontal axis. The electric field \(\vec{E}\)  and the wave vector  \(\vec{k}\) are shown by the green and yellow arrows, respectively. The normalized GDI growth rate at every cell in the radar's FoV was calculated and the radar cells are colored accordingly, with the color bar shown in the bottom-right corner.  The \(E\) region, transitional region, and \(F\) region are outlined in red, green, and blue, respectively.}
	\label{fig:model_setup}
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{p2f2.pdf}
	\caption[GDI growth rate within radar FoV]{{\:}GDI growth rate within radar FoV\\ The GDI growth rate within the radar's FoV for four cases of gradient reversal orientation and position (white line).  In all cases, the convection direction \(\vec{V}_E\) (red arrow) is perpendicular to the gradient reversal direction.  The orientation of the vectors \(\vec{G}\), \(\vec{V}_E\), \(\vec{E}\), and \(\vec{k}\) are shown in each panel, using the same colors as in Figure \ref{fig:model_setup}c.  The GDI growth rate at each radar cell is given by the cell color, with the color bar given in the bottom-left corner of panel (a). Panels (a) and (b) show a gradient reversal centered in the \(F\) region, while panels (c) and (d) show the reversal in the transitional region.  The angles \(\theta\) and \(\phi\) (as defined in Figure \ref{fig:model_setup}c) are also given in the bottom-right corner of each panel.}
	\label{fig:fov_grs}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f3.pdf}
	\caption[GDI growth rates for set angle between \(\vec{V}_E\) and \(\vec{G}\)]{{\:}GDI growth rates for set angle between \(\vec{V}_E\) and \(\vec{G}\)\\ The difference in the GDI growth rate across the gradient reversal for four selected angles between the reversal and convection direction.  The gradient reversal direction \(\theta\) is on the \(x\)-axis and the average growth rate difference across the reversal \(\Delta\gamma\) is on the \(y\)-axis for each panel.  The difference between \(\phi\) and \(\theta\) is given in the top-right corner of each plot. The difference in the average growth rate \(\Delta\gamma\) computed using a numerical approach (see text for details) is shown by the solid lines, with the shaded regions representing the standard deviation.  The dashed lines show the behavior of \(\Delta\gamma\) calculated using an analytic expression. The trends for both the \(E\)-region (red) and \(F\)-region (blue) cases are shown in each panel.}
	\label{fig:set_angle}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f4.pdf}
	\caption[GDI growth rates for arbitrary angle between \(\vec{V}_E\) and \(\vec{G}\)]{{\:}GDI growth rates for arbitrary angle between \(\vec{V}_E\) and \(\vec{G}\)\\ Contour plots of the growth rate difference \(\Delta\gamma\)  versus the two angles of interest. The direction of the gradient reversal \(\theta\) is on the \(x\)-axis and the convection direction \(\phi\) is on the \(y\)-axis.  The color bar is given to the right. Panels (a) and (b) show the results using an analytic approach in the \(E\) and \(F\) regions, respectively.  Panels (c)--(f) show the results using a numerical approach in the \(E\), \(F\), transitional, and all regions, respectively. The dashed black and white line in panels (c) and (f) indicates the average value of the conductivity ratio \(R\) along the gradient reversal for different angles \(\theta\) in the transitional region and all regions, respectively. The scale for \(R\) is shown on the right of panels (c) and (f).}
	\label{fig:any_angle}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth,angle=180]{p2f5.pdf}
	\caption[GDI growth rate within transitional region]{{\:}GDI growth rate within transitional region\\ Analysis of the transitional region.  (a) The average conductivity ratio \(R\) (black line) and the radar virtual height (orange line) versus the slant range for the entire transitional region and parts of the \(E\) and \(F\) regions. The scales for the conductivity ratio and height are given on the left and right of panel (a), respectively.  The \(E\) (red), transitional (yellow and green) and \(F\) (blue) regions are highlighted.  The region highlighted with yellow is examined closer in panels (b) and (c).  Panel (b) is similar to panel (a), but focuses on slant ranges 600--616 km, where most of the change in the conductivity ratio occurs.  In addition to the \(R\) and height continuous variations, it also gives the average value of \(R\) for each 2-km virtual range gate. The same 2-km virtual gates are considered in panel (c) that shows a similar analysis to Figure \ref{fig:any_angle}. The top row shows the results of the numerical approach (N) and the bottom row shows the analytic approach results (A).}
	\label{fig:transitional}
\end{figure}
